Gravitational field calculation in spherical coordinates using variable densities in depth

### 2019-04-04 manuscript/manuscript.tex
Minor typos

Both the \citet{Lin2018} and the \citet{Fukushima2018} studies limit the radial density
variation to polynomial functions.
While most continuous and smooth functions can be approximated by piecewise linear
functions, the choice of a discretization interval is neither straight forward nor
automatic.
Furthermore, it is well known that the use of high-degree polynomials to approximate a
highly variable function produces unstable results when extrapolating beyond the data
domain.
These shortcomings could make piecewise linear or high-degree polynomial density
functions unwieldy for non-linear gravity inversions \citep[e.g.][]{Uieda2017} if the
density function in depth is highly variable.

@@

\textit{Step 1}: Check that the tesseroid satisfies the following inequality for its
latitudinal and longitudinal dimensions $L_i\ (i \in \{\lambda, \phi\})$:

>>>>

Both the \citet{Lin2018} and the \citet{Fukushima2018} studies limit the radial density
variation to polynomial functions.
While most continuous and smooth functions can be approximated by piecewise linear
functions, the choice of a discretization interval is neither straight forward nor
automatic for the general case.
Although many piecewise linear approximation algorithms that automate this process
exist \citep{Ketkov1969, Vandewalle1975, Imamoto2008, Ahmadi2013}, they either require
a fixed number of discretization intervals or are meant to be used only on convex
functions.
Using such algorithms would limit the range of density functions that can be assigned 
to the tesseroids and would not guarantee a fully automatic process.
Furthermore, it is well known that the use of high-degree polynomials to approximate a
highly variable function produces unstable results when extrapolating beyond the data
domain.
These shortcomings could make piecewise linear or high-degree polynomial density
functions unwieldy for non-linear gravity inversions \citep[e.g.][]{Uieda2017} if the
density function in depth is highly variable.

@@

\textit{Step 1}: Check that the tesseroid satisfies the following inequality for each
dimension $L_i\ (i \in \{\lambda, \phi\})$ of the tesseroid:
